---
 title: "Life Expectation and GDP"
 subtitle: "Do people living in rich country live longer?"
 output:
   xaringan::moon_reader:
     lib_dir: libs
     nature:
       highlightStyle: github
       highlightLines: true
       countIncrementalSlides: false
---
 
```{r, setup, echo = F, message = F, warning = F, fig.align='center'}
library(tidyverse)
knitr::opts_chunk$set(
  fig.width = 10, fig.height = 5, fig.align = 'center'
  ) 
```
 
# Definition

### Gross domestic product (GDP):

the total monetary or market value of all the finished goods and services produced within a country’s borders in a specific time period. As a broad measure of overall domestic production, it functions as a comprehensive scorecard of a given country’s economic health.

--

### Life expectancy:

a statistical measure of the average time an organism is expected to live, based on the year of its birth, its current age, and other demographic factors including biological sex.
 
---

# Data 
This table includes 7 countries, their life expectancy and GDP per Capita in year 2008.

```{r, echo = F, message = F}
library(gapminder)
library(tidyverse)
library(dplyr)
library(kableExtra)
tib <- gapminder
column <- c(1,3,4,6)
tib <- tib[,column]
current_year <- 2007
tib_filtered <- tib %>% 
  filter(year == current_year) %>%
  filter(country %in% c(
    "Germany", 
    "Australia",
    "United States",
    "Afghanistan",
    "Bangladesh",
    "Romania",
    "Zambia"
  ))

knitr::kable(tib_filtered, booktabs ="T") %>%
  kable_styling(bootstrap_options = "striped", position = "left") %>%
  row_spec(6, background = "yellow") %>%
  row_spec(7, background = "yellow")
```

???
the data is from package: gapminder
 
---

# Figure

The figure shows the relationship between lifeExp and gdpPerCap based the data of five continents in 2007.

```{r, echo = F, message = F}
library(gapminder)
library(tidyverse)

tib <- gapminder

current_year <- 2007
tib_filtered <- tib %>% 
  filter(year == current_year)
tib_filtered %>%
  ggplot() +
  geom_point(mapping = aes(x = gdpPercap, y = lifeExp, color = continent))
  
```
 

We can see that GDP per Capcita is larger then the life expectancy is larger.